---
title: Setup for R workshops
---

```{r include-setup-r, child="files/setup-r.md"}
```

## Software

| Software            | Install                         | Manual | Available for         | Description                                               | 
| ------------------- | ------------------------------- | ------ | --------------------- | --------------------------------------------------------- |
| Spreadsheet program | [Link](https://www.libreoffice.org/download/download/)                                | [Link](https://documentation.libreoffice.org/en/english-documentation/)       | Linux, MacOS, Windows | Spreadsheet program for organizing tabular data.          | 
| OpenRefine          | [Link](http://openrefine.org/download.html)                                | [Link](http://openrefine.org/documentation.html)       | Linux, MacOS, Windows | Program for reproducibly cleaning data.                   | 
| R                   | See install instructions below. |        | Linux, MacOS, Windows | Programming language for data analysis and visualisation. | 
| RStudio             | [Link](https://www.rstudio.com/products/rstudio/download/#download)                                | [Cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/rstudio-ide.pdf)       | Linux, MacOS, Windows | Integrated development environment for R.                 | 
| SQLite Browser      | [Link](http://sqlitebrowser.org/dl/)                                | [Link](https://github.com/sqlitebrowser/sqlitebrowser/wiki)       | Linux, MacOS, Windows | Tool for creating, designing, and editing database files. | 

```{r include-setup-sql, child="files/setup-sql.md"}
```

```{r include-setup-data, child="files/setup-data.md"}
```

```{r include-setup-spreadsheet, child="files/setup-spreadsheet.md"}
```

```{r include-setup-openrefine, child="files/setup-openrefine.md"}
```

Congratulations! You are now ready for the workshop!


